\paperTitle

### 2014-05-01 doc/icml2014/icml2014-presentation/diagrams.tex
Updated presentation

% Hidden nodes
   \node[style=node, scale=0.8] (h1) at (0,0) {$h_1$};
   \node[style=node, scale=0.8] (h2) at (-1.3cm,-1cm) {$h_2$};
   \node[style=node, scale=0.8] (h3) at (0,   -1cm) {$h_3$};
   \node[style=node, scale=0.8] (h4) at (1.3cm, -1cm) {$h_4$};

@@

% Observed nodes
  \node[style=obsnode, scale=0.7] (x2a) at (-1.6cm, -2.0cm) {$x^a_2$};
  \node[style=obsnode, scale=0.7] (x2b) at (-1.0cm, -2.0cm) {$x^b_2$};
  \draw[-latex] (h2) -- (x2a);
  \draw[-latex] (h2) -- (x2b);

  \node[style=obsnode, scale=0.7] (x3a) at (-0.3cm, -2.0cm) {$x^a_3$};
  \node[style=obsnode, scale=0.7] (x3b) at (0.3cm, -2.0cm) {$x^b_3$};
  \draw[-latex] (h3) -- (x3a);
  \draw[-latex] (h3) -- (x3b);

  \node[style=obsnode, scale=0.7] (x4a) at (1.0cm, -2.0cm) {$x^a_4$};
  \node[style=obsnode, scale=0.7] (x4b) at (1.6cm, -2.0cm) {$x^b_4$};
  \draw[-latex] (h4) -- (x4a);
  \draw[-latex] (h4) -- (x4b);
  }
}

>>>>

% Hidden nodes
   \node[style=node, scale=0.8] (h1) at ($(start-tree) + (0,0)$) {$h_1$};
   \node[style=node, scale=0.8] (h2) at ($(start-tree) + (-1.3cm,-1cm)$) {$h_2$};
   \node[style=node, scale=0.8] (h3) at ($(start-tree) + (0,   -1cm)$) {$h_3$};
   \node[style=node, scale=0.8] (h4) at ($(start-tree) + (1.3cm, -1cm)$) {$h_4$};

@@

% Observed nodes
  \node[style=obsnode, scale=0.7] (x2a) at ($(start-tree) + (-1.6cm, -2.0cm)$) {$x^a_2$};
  \node[style=obsnode, scale=0.7] (x2b) at ($(start-tree) + (-1.0cm, -2.0cm)$) {$x^b_2$};
  \draw[-latex] (h2) -- (x2a);
  \draw[-latex] (h2) -- (x2b);

  \node[style=obsnode, scale=0.7] (x3a) at ($(start-tree) + (-0.3cm, -2.0cm)$) {$x^a_3$};
  \node[style=obsnode, scale=0.7] (x3b) at ($(start-tree) + (0.3cm, -2.0cm)$) {$x^b_3$};
  \draw[-latex] (h3) -- (x3a);
  \draw[-latex] (h3) -- (x3b);

  \node[style=obsnode, scale=0.7] (x4a) at ($(start-tree) + (1.0cm, -2.0cm)$) {$x^a_4$};
  \node[style=obsnode, scale=0.7] (x4b) at ($(start-tree) + (1.6cm, -2.0cm)$) {$x^b_4$};
  \draw[-latex] (h4) -- (x4a);
  \draw[-latex] (h4) -- (x4b);
  }
}

\newcommand<>{\drawnoisyor}[1]  {
\uncover#2{
\point{start-nor}{#1}
\node[style=node, scale=0.8] (h1) at ($(start-nor) + (-0.5,0)$) {$h_1$};
   \node[style=node, scale=0.8] (h2) at ($(start-nor) + (+0.5,0)$) {$h_2$};
   \node[style=obsnode, scale=0.8] (x1) at ($(start-nor) + (-2.0, -1.0)$) {$x_1$};
   \node[style=obsnode, scale=0.8] (x2) at ($(start-nor) + (-1.0, -1.0)$) {$x_2$};
   \node[style=obsnode, scale=0.8] (x3) at ($(start-nor) + (0.0, -1.0) $){$x_3$};
   \node[style=obsnode, scale=0.8] (x4) at ($(start-nor) + (1.0, -1.0) $){$x_4$};
   \node[style=obsnode, scale=0.8] (x5) at ($(start-nor) + (2.0, -1.0) $){$x_5$};

   \draw[-latex] (h1) -- (x1);
   \draw[-latex] (h1) -- (x2);
   \draw[-latex] (h1) -- (x3);

   \draw[-latex] (h2) -- (x2);
   \draw[-latex] (h2) -- (x3);
   \draw[-latex] (h2) -- (x4);
   \draw[-latex] (h2) -- (x5);
   }
}
